---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Fedor Miasnikov (12886680)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1

### d)

Strengths:
- git enables collaboration with other software developers.
- git allows one to track the history of changes made to a document.

Weaknesses:
- the history of changes takes up file space.
- git doesn't work in the background and the commands always have to be executed manually.

## Exercise 2

### a)

https://github.com/Crazy-fm-1/exeRcise-sheet-3

## Exercise 3

### a)

```{r}
library(tidyverse)
pixar <- read_csv("pixar_films.csv") %>% filter(!is.na(film))
pixar$film_rating <- as.factor(pixar$film_rating)
```

The variable film_rating has the possible values G, PG and N/A. G stands for general audiences and means that the movie may be viewed by individuals of any age. PG stands for parental guidance suggested and advises parents to check whether the movie contains any content they wouldn't want their children to see before letting said children view it. N/A means that the movie hasn't received a rating.

It is appropriate to store this variable as a factor because it is nominal and has a limited number of possible values.

### b)

```{r}
series <- tibble(
  series = c("Toy Story", "Toy Story", "Toy Story", "Toy Story",
  "Cars", "Cars", "Cars", "The Incredibles", "The Incredibles"),
  title = c("Toy Story", "Toy Story 2", "Toy Story 3",
  "Toy Story 4", "Cars", "Cars 2", "Cars 3", "The Incredibles",
  "The Incredibles 2"),
  series_length = c(4, 4, 4, 4, 3, 3, 3, 2, 2))
print(series)
```

### c)

```{r}
resp <- read_csv("public_response.csv")
resp$cinema_score <- factor(resp$cinema_score, levels = c("A-", "A", "A+"))
movies <- left_join(pixar, resp, by = "film")
```