---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Fedor Miasnikov (12886680)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1

### d)

Strengths:
- git enables collaboration with other software developers.
- git allows one to track the history of changes made to a document.

Weaknesses:
- The history of changes takes up file space.
- git doesn't work in the background and the commands always have to be executed manually.

## Exercise 2

### a)

https://github.com/Crazy-fm-1/exeRcise-sheet-3

## Exercise 3

### a)

```{r}
library(tidyverse)
pixar <- read_csv("pixar_films.csv") %>% filter(!is.na(film))
pixar$film_rating <- as.factor(pixar$film_rating)
```

The variable film_rating has the possible values G, PG and N/A. G stands for general audiences and means that the movie may be viewed by individuals of any age. PG stands for parental guidance suggested and advises parents to check whether the movie contains any content they wouldn't want their children to see before letting said children view it. N/A means that the movie hasn't received a rating.

It is appropriate to store this variable as a factor because it is nominal and has a limited number of possible values.

### b)

```{r}
series <- tibble(
  series = c("Toy Story", "Toy Story", "Toy Story", "Toy Story",
  "Cars", "Cars", "Cars", "The Incredibles", "The Incredibles"),
  film = c("Toy Story", "Toy Story 2", "Toy Story 3",
  "Toy Story 4", "Cars", "Cars 2", "Cars 3", "The Incredibles",
  "The Incredibles 2"),
  series_length = c(4, 4, 4, 4, 3, 3, 3, 2, 2))
print(series)
```

### c)

```{r}
resp <- read_csv("public_response.csv")
resp$cinema_score <- factor(resp$cinema_score, levels = c("A-", "A", "A+"))
movies <- left_join(pixar, resp, by = "film")
```

### d)

```{r}
series <- left_join(series, resp, by = "film")

series %>% filter(!is.na(metacritic)) %>%
ggplot() +
  geom_bar(aes(y = film, x = metacritic, fill = series),
           position = "dodge", stat = "identity") +
  labs(fill = "", y = "Movie title", x = "Metacritic rating",
       title = "Metacritic ratings of Pixar series") +
  theme(
    plot.title = element_text(hjust = 0.5)
  )
```

In general, later releases within a given series tend to have lower Metacritic scores compared to earlier ones.

## Exercise 4

### b)

```{r}
vac <- read_csv("Vaccine Coverage and Disease Burden - WHO (2017).csv") %>% janitor::clean_names()
```

### c)

- Dataset name: Vaccine Coverage and Disease Burden - WHO (2017)
- Link: https://github.com/owid/owid-datasets/tree/master/datasets/Vaccine%20Coverage%20and%20Disease%20Burden%20-%20WHO%20(2017)

### d)

Lately, measles rates have been rising in certain areas of the world, including some parts of the US, as debates about the effectiveness of measles vaccines continue.

I'm interested in the correlation between the measles (MCV) immunization coverage among one year old children and the number of confirmed measles cases in a given year. Though this measure is imperfect, it can provide some information about the effectiveness of measles-containing vaccines. I've chosen to examine the data for Africa as it still remains a hotbed for measles.

### e) and f)

```{r measles, fig.cap="Measles immunization coverage and confirmed measles cases in Africa"}
options(scipen = 999)
afr <- vac %>% filter(entity == "Africa" &
  !is.na(measles_mcv_immunization_coverage_among_1_year_olds_who_2017) &
  !is.na(number_of_confirmed_measles_cases_who_2017)) %>%
  select(entity, measles_mcv_immunization_coverage_among_1_year_olds_who_2017,
  number_of_confirmed_measles_cases_who_2017, year) %>%
  rename(vac_rate = measles_mcv_immunization_coverage_among_1_year_olds_who_2017) %>%
  rename(cases = number_of_confirmed_measles_cases_who_2017)

stand_afr <- afr %>%
  mutate(vac_rate = (vac_rate - min(vac_rate)) / (max(vac_rate) - min (vac_rate)),
  cases = (cases - min(cases)) / (max(cases) - min (cases))
  )

sup <- tibble(year = c(2014, 2014, 2015, 2015),
  cat = c("Measles (MCV) immunization coverage among one year old children",
  "Number of confirmed measles cases", 
  "Measles (MCV) immunization coverage among one year old children",
  "Number of confirmed measles cases"),
  value = c(0.97058824, 0.02681496, 1, 0.01143898))

ggplot(data = stand_afr) +
  geom_line(aes(x = year, y = vac_rate),
  color = "red") +
  geom_line(aes(x = year, y = cases, linetype = ),
  color = "blue") +
  scale_y_continuous(labels = c("0%", "20%", "40%", "60%", "80%", "100%"),
  breaks = ((seq(0, 100, 20) - min(afr$vac_rate)) / (max(afr$vac_rate) - min (afr$vac_rate))),
  limits = (c(0, 80) - min(afr$vac_rate)) / (max(afr$vac_rate) - min (afr$vac_rate)),
  sec.axis = sec_axis(~.,
  labels = seq(0, 1500000, 300000),
  breaks = (seq(0, 1500000, 300000) - min(afr$cases)) / (max(afr$cases) - min (afr$cases))
  )
  ) +
  geom_line(data = sup, aes(x = year, y = value, color = cat)) +
  scale_color_manual(labels = c("Measles (MCV) immunization coverage\namong one year old children",
  "Number of confirmed measles cases"), values = c("red", "blue")) +
  labs(color = "", x = "Year", y = "") +
  theme(
  axis.text.y.left = element_text(color = "red"),
  axis.text.y.right = element_text(color = "blue")
  )
```

Figure \@ref(fig:measles) indicates a strong, linear, negative correlation between the measles (MCV) immunization coverage among one year old children and the number of yearly confirmed measles cases. The Pearson correlation coefficient for these variables is `r round(cor(afr$vac_rate, afr$cases), 3)`, which substantiates this claim.

To further investigate the effect of measles vaccination on the number of confirmed measles cases, I construct a linear model with the measles (MCV) immunization coverage among one year old children as the independent variable and the number of yearly confirmed measles cases as the dependent variable.

```{r}
model <- lm(cases ~ vac_rate, data = afr)
library(stargazer)
stargazer(model, type = "text", ci = TRUE, star.cutoffs = c(0.05, 0.01, 0.001), ci.level = 0.95)
```

This model indicates that, if the measles vaccination rate among one year old children increases by 1% c. p., we expect the number of yearly confirmed measles cases to fall by 21378.53. This is statistically significant on a 0.1% level. The values for R^2^ and adjusted R^2^ show that the measles vaccination rate among one year old children is able to explain over 92% of the variability of the yearly confirmed measles cases.

Thus, the results of this investigation hint that increasing measles (MCV) immunization coverage among one year old children could cause a reduction in the yearly number of confirmed measles cases. This stands as an argument for the general effectiveness of measles vaccines at preventing measles infection.